# Reproducible Research: Peer Assessment 1
==========================================

## Loading and preprocessing the data
--------------------------------------

* Load the data
```{r echo=TRUE}
  activity <- read.csv("activity.csv")
```

* Process/transform the data (if necessary) into a format suitable for your analysis
```{r echo=TRUE}
  totalSteps <- aggregate(steps~date,data=activity,sum,na.rm=TRUE)
```

## What is mean total number of steps taken per day?
----------------------------------------------------

* Make a histogram of the total number of steps taken each day
```{r}
  hist(totalSteps$steps,col="blue",xlab="Total Steps per Day",ylab="Frequency", main="Histogram of Total Steps taken per day")
 
```

* Calculate and report the mean and median total number of steps taken per day
```{r echo=TRUE}
  showMean <- mean(totalSteps$steps)
  showMedian <- median(totalSteps$steps)
```
* The **mean** total number of steps taken per day is `r showMean` steps.
* The **median** total number of steps taken per day is `r showMedian` steps.


## What is the average daily activity pattern?
----------------------------------------------

* Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r echo=TRUE}
  stepsInterval<-aggregate(steps~interval,data=activity,mean,na.rm=TRUE)
  plot(steps~interval,data=stepsInterval,type="l",xlab="Time Intervals (5-minute)", 
     ylab="Mean number of steps taken (all Days)", 
     main="Average number of Steps Taken at different 5 minute Intervals",
     col="red")
```

* Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? 
```{r}
  showStepInterval <- stepsInterval[which.max(stepsInterval$steps),]$interval
```
* It is the **`r showStepInterval `th** interval.

## Imputing missing values
---------------------------

* Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r echo=TRUE}
  showSum <- sum(is.na(activity))
```
Total `r showSum` rows are missing.

* Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r echo=TRUE}
    interval2steps<-function(interval){
      stepsInterval[stepsInterval$interval==interval,]$steps
    }
```

* Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo=TRUE}
  activityFilled <- activity
  count=0
  for(i in 1:nrow(activityFilled)){
    if(is.na(activityFilled[i,]$steps)){
        activityFilled[i,]$steps<-interval2steps(activityFilled[i,]$interval)
        count=count+1
    }
  }
  cat("Total ",count, "NA values were filled.\n")  
```

* Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r echo=TRUE}
  totalStepsPerDays<-aggregate(steps~date,data=activityFilled,sum) 
  hist(totalStepsPerDays$steps,col="green",xlab="Total Number of Steps",ylab="Frequency", main="Histogram of Total Number of Steps taken each Day")
  mean(totalStepsPerDays$steps)
  median(totalStepsPerDays$steps)
```
* The **mean** total number of steps taken per day is `r mean(totalStepsPerDays$steps)` steps.
* The **median** total number of steps taken per day is `r median(totalStepsPerDays$steps)` steps.

*Do these values differ from the estimates from the first part of the assignment?What is the impact of imputing missing data on the estimates of the total daily number of steps?
: The **mean** value is the **same** as the value before imputing missing data because we put the mean value for that particular 5-min interval. The median value shows **a little** difference : but it depends on **where the missing values are**.

## Are there differences in activity patterns between weekdays and weekends?
-------------------------------------------------------------------------------
* Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r echo=TRUE}
  activityFilled$day=ifelse(as.POSIXlt(as.Date(activityFilled$date))$wday%%6==0,"weekend","weekday")
  # For Sunday and Saturday : weekend, Other days : weekday 
  activityFilled$day=factor(activityFilled$day,levels=c("weekday","weekend"))
```

* Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). The plot should look something like the following, which was creating using simulated data:
```{r echo=TRUE}
  stepsInterval2=aggregate(steps~interval+day,activityFilled,mean)
  library(lattice)
  xyplot(steps~interval|factor(day),data=stepsInterval2,aspect=1/2,type="l")
```
